---
title: "Intro to packagelab5"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to packagelab5}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This vignette is an introduction to the package packagelab5.
packagelab5 helps you navigate through the Kolada api. The Kolada api allows you to access the Kolada database which contains key indicators regarding the Swedish municipalities. More information can be found [here](https://www.kolada.se/).
Also, other useful information can be found [here](https://github.com/duckduckquack/packagelab5.git)

## 1) Aim of the package
This package contains useful functions to help you navigate through the Kolada api and get data from it. 

## 2) Functionalities 
The package contains 5 functions: get_city_id, get_data, get_kpi_desc, get_kpi_id, and get_kpi_title. 

## 3) How to load the package
The package can be loaded as follows:
```{r setup}
library(packagelab5)
```

## 4) get_city_id
get_city_id takes as input the name of a Swedish municipality as a string and returns the correponding id in the Kolada api:
```{r}
get_city_id("Ale")
```
or 
```{r}
get_city_id("ale")
```

The name of the municipality has to be exact as the function does not allow for partial matching. 

## 5) get_data
get_data takes as input a kpi id, a set of years and a municipality id. It then returns the corresponding data as a data frame:
```{r}
get_data(kpi_id = "N00403", year = "2020,2021", city_id = "0580")
```
In this case, it returns the data regarding the organic farmland share in % in the years 2020 and 2021 for the Linkoping municipality.

## 6) get_kpi_desc
get_kpi_desc returns a brief description of the kpi given the kpi title:
```{r}
get_kpi_desc("Ekologiskt odlad \u00e5kermark, andel (%)")
```
## 7) get_kpi_id 
get_kpi_id returns the id of a kpi given its title:
```{r}
get_kpi_id("Ekologiskt odlad \u00e5kermark, andel (%)")
```
## 8) get_kpi_title
get_kpi_title is the opposite of get_kpi_id. Given a kpi title it returns the corresponding id:
```{r}
get_kpi_title("N00403")
```
